---
title: "Programa de Prevención y Control del Dengue en Jalisco"
output: 
  flexdashboard::flex_dashboard:
      theme: united
      social: ["twitter", "facebook", "menu", "github"]
output_dir: libs      
---

```{r setup}

# Step 1. load the library ####
options(shiny.maxRequestSize=30*1024^2)
library(formattable)
library(tmap)
library(rmarkdown)
library(knitr)
library(shiny)
library(flexdashboard)
library(plotly)
library(boldenr)
library(magrittr)
library(leaflet)
library(ggplot2)
library(dplyr)
library(stringr)
#library(dash)
library(ECharts2Shiny)
library(sf)

# Step 3. load the functions ####
if(as.vector(Sys.info()["sysname"]) == "Darwin"){
    
    # 1.6 hotspots cases
    source("~/Dropbox/r_developments/r_new_functions/3.Functions/risk_agebs.R")
    
    source("~/Dropbox/r_developments/r_new_functions/3.Functions/risk_map.R")
    
    source("~/Dropbox/r_developments/r_new_functions/3.Functions/hotspots_map.R")
    
    # 1. 7 eggs hotspots ####
    
    source("~/Dropbox/r_developments/r_dashboards/github_pages/test_denv_dash_oax/3.Functions/eggs_hotspots_intensity_map_year.R")

    
} else if(as.vector(Sys.info()["sysname"]) == "Windows"){
    # 1.1. dengue dataset
    
    # 1.5 ulv dataset
    
    # 1.6 hotspots


    #Step  load the risk_ageb function ###
    source('C:/Users/HOME/Dropbox/r_developments/r_dashboards/github_pages/test_dashboard/3.Functions/risk_agebs.R')

    # Step  load the risk_map function ####
    source("D:/OneDrive/proyects/hotspots/3.Functions/risk_map.R")

    # Step  load the hotspots map ####
    source("C:/Users/HOME/Dropbox/r_developments/r_dashboards/github_pages/test_dashboard/3.Functions/hotspots_map.R")
    
    # 1. 7 eggs hotspots ####
    source("C:/Users/HOME/Dropbox/r_developments/r_dashboards/github_pages/test_denv_dash_oax/3.Functions/eggs_hotspots_intensity_map_year.R")
    
} else if(as.vector(Sys.info()["sysname"]) == "Linux"){
    
}



# Step 5. Load the RData files ####
if(as.vector(Sys.info()["sysname"]) == "Darwin"){
     
    # Step 1. load the dengue cases hotspots ####
    load("~/Library/CloudStorage/Dropbox/hotspots_2022/8.RData/cases_hotspots_agebs19.RData")
    hotspots <- cases_hotspots_agebs19 |>
    sf::st_make_valid()
    
    # Step 2. load the vector hotspots ####
    load("~/Library/CloudStorage/OneDrive-Personal/proyects/hotspots_eggs/8.RData/14_jalisco/betas/14_jalisco_zinb1_betas.RData")
    
    
} else if(as.vector(Sys.info()["sysname"]) == "Windows"){
    
    # Step 1. load the hotspots dengue cases ####
   load("E:/backup/Dropbox_respaldo_2023_01_03/hotspots_2022/8.RData/cases_hotspots_agebs19.RData")
    
    cases_hotspots_agebs19 <- cases_hotspots_agebs19 |>
    sf::st_make_valid()

    
    # Step 2. load the vector hotspots
     
    
} else if(as.vector(Sys.info()["sysname"]) == "Linux"){
    
}


```

# **Hotspots de la Transmisión de Dengue**

## Column {.tabset}

### [**Guadalajara**]{style="color:#990000"}

```{r, hotspots_dengue_cuernavaca, echo=FALSE}
hotspots_map(cve_ent = "14",
             locality = c("Guadalajara",
                          "Tlaquepaque",
                         "Zapopan", 
                         "Tonalá"),
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```

### [**Puerto Vallarta**]{style="color:#990000"}

```{r, hotspots_dengue_puerto_vallarta, echo=FALSE}
hotspots_map(cve_ent = "14",
             locality = "Puerto Vallarta",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```

### [**Ciudad Guzmán**]{style="color:#990000"}

```{r, hotspots_dengue_ciudad_guzman, echo=FALSE}
hotspots_map(cve_ent = "14",
             locality = "Ciudad Guzman",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```

### [**Autlán**]{style="color:#990000"}

```{r, hotspots_dengue_autlan_navarro, echo=FALSE}
hotspots_map(cve_ent = "14",
             locality = "Autlán de Navarro",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)
```

### [**Cihuatlan**]{style="color:#990000"}

```{r, hotspots_dengue_cihuatlan, echo=FALSE}
hotspots_map(cve_ent = "14",
             locality = "Cihuatlán",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```


# **Hotspots del Vector del Dengue**

## Column {.tabset}

### **<span style="color:#990000">Guadalajara</span>**
```{r vector_hotspots_guadalajara, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_14_jalisco,
                                 locality = c("Guadalajara",
                                              "Tlaquepaque",
                                              "Zapopan", 
                                              "Tonalá"),
                                 cve_ent = "14",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

### **<span style="color:#990000">Puerto Vallarta</span>**
```{r vector_hotspots_vallarta, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_14_jalisco,
                                 locality = "Puerto Vallarta",
                                 cve_ent = "14",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```


### **<span style="color:#990000">Autlan</span>**
```{r vector_hotspots_autlan, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_14_jalisco,
                                 locality = "Autlan de Navarro",
                                 cve_ent = "14",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```


### **<span style="color:#990000">La Barca</span>**
```{r vector_hotspots_barca, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_14_jalisco,
                                 locality = "La barca",
                                 cve_ent = "14",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

### **<span style="color:#990000">Cihuatlan</span>**
```{r vector_hotspots_cihuatlan, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_14_jalisco,
                                 locality = "Cihuatlán",
                                 cve_ent = "14",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

### **<span style="color:#990000">Tequila</span>**
```{r vector_hotspots_tequila, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_14_jalisco,
                                 locality = "Tequila",
                                 cve_ent = "14",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```


# **Mapa del Riesgo de Transmisión del Dengue**

## Column {.tabset}

### [**Guadalajara**]{style="color:#7d9029"}

```{r risk_map_guadalajara, echo=FALSE}
risk <- risk_agebs(spde_model = betas_14_jalisco,
                   hotspots = cases_hotspots_agebs19,
                   locality = c("Guadalajara",
                                "Tlaquepaque",
                                "Zapopan", 
                                "Tonalá"),
                   cve_ent = "14",
                   intensity_perc = 25)
risk_map(risk = risk,
         staticmap = FALSE)
```


### [**Puerto Vallarta**]{style="color:#7d9029"}

```{r risk_map_vallarta, echo=FALSE}
risk <- risk_agebs(spde_model = betas_14_jalisco,
                   hotspots = cases_hotspots_agebs19,
                   locality = "Puerto Vallarta",
                   cve_ent = "14",
                   intensity_perc = 25)
risk_map(risk = risk,
         staticmap = FALSE)
```

### [**Autlan**]{style="color:#7d9029"}

```{r risk_map_autlan, echo=FALSE}
risk <- risk_agebs(spde_model = betas_14_jalisco,
                   hotspots = cases_hotspots_agebs19,
                   locality = "Autlan de Navarro",
                   cve_ent = "14",
                   intensity_perc = 25)
risk_map(risk = risk,
         staticmap = FALSE)
```

### [**Cihuatlán**]{style="color:#7d9029"}
```{r risk_map_cihuatlan, echo=FALSE}
risk <- risk_agebs(spde_model = betas_14_jalisco,
                   hotspots = cases_hotspots_agebs19,
                   locality = "Cihuatlán",
                   cve_ent = "14",
                   intensity_perc = 25)
risk_map(risk = risk,
         staticmap = FALSE)
```

### [**Ciudad Guzman**]{style="color:#7d9029"}
```{r risk_map_cd_guzman, echo=FALSE}
risk <- risk_agebs(spde_model = betas_14_jalisco,
                   hotspots = cases_hotspots_agebs19,
                   locality = "Ciudad Guzman",
                   cve_ent = "14",
                   intensity_perc = 25)
risk_map(risk = risk,
         staticmap = FALSE)
```
